Case for Support

### 2021-11-16 application/backgroundToTheResource.tex

@@

\setlength{\columnsep}{1em}
\begin{wrapfigure}{R}{0.6\textwidth}
    \href{http://www.gatsby.ucl.ac.uk/~rapela/bbsrc-bbr21/roadmap-bbsrc_noCaption.png}{\includegraphics[width=0.6\textwidth]{figures/roadmap-bbsrc_noCaption.png}}

  \caption{\small Bonsai development timeline and community adoption. (A) Timeline of
    milestones and landmark package releases. (B) Example capabilities 
    within Bonsai. (C) Bonsai workflow for tracking the position of objects
    in a video. (D) Worldwide
    distribution of visitors to the bonsai-rx.org website. (E)
    Number of downloads for each Bonsai version. (F) Cumulative number of
    registered forum users, citations of the main publication, and number of
    training events, by year (bottom panels), versus release and development
    cycle (top panel), measured in commits to main repository. Click on the
    image to see its online version.}

  \label{fig:bonsai}

\end{wrapfigure}

>>>>

\setlength{\columnsep}{1em}
\begin{wrapfigure}{R}{0.5\textwidth}
    \href{http://www.gatsby.ucl.ac.uk/~rapela/bbsrc-bbr21/roadmap-bbsrc_noCaption.png}{\includegraphics[width=0.5\textwidth]{figures/roadmap-bbsrc_noCaption.png}}

  \caption{\footnotesize Bonsai development timeline and community adoption. (A) Timeline of
    milestones and landmark package releases. (B) Example capabilities 
    within Bonsai. (C) Bonsai workflow for tracking the position of objects
    in a video. (D) Worldwide
    distribution of visitors to the bonsai-rx.org website. (E)
    Number of downloads for each Bonsai version. (F) Cumulative number of
    registered forum users, citations of the main publication, and number of
    training events, by year (bottom panels), versus release and development
    cycle (top panel), measured in commits to main repository. 
    % Click on the image to see its online version.
    }

  \label{fig:bonsai}
\end{wrapfigure}

@@
